Hybrid platforms and bargaining power

### 2023-02-06 src/paper/application.tex
Add preliminary results

\begin{proposition}

\end{proposition}

@@

This section introduces the modeling framework used throughout the paper.
I start by describing the demand system of a continuum of consumers and differentiated, monopolistically competitive sellers \parencite[]{anderson2021hybrid}.
After that, I describe the role of the (potentially hybrid) platform on this market.

>>>>

Some preliminary (hand-wavily proven) results about equilibrium profits and entry.

\begin{proposition}
    \label{prop:share_of_platform}
    Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
    Then $\pi_P$ is also differentiable and
    $$\frac{\partial \pi_P(N_P, n_F)}{\partial N_P} > 0$$.
\end{proposition}

\begin{proposition}
    \label{prop:share_of_fringe}
    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
    Then $\pi_F$ is also differentiable. Let $N_F > 0$.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
        &\text{if } \frac{\partial^2 f(N_P, N_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
    \end{align*}
    for all $N_P \geq 0$.
\end{proposition}

\begin{corollary}
    \label{fringe_entry}
    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
    Let $N_F^*$ denote the equilibrium number of fringe firms.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
    \end{align*}
\end{corollary}

@@

This section presents an example application of the model, based on \parencite[]{anderson2021hybrid}.
The setting is a (possibly hybrid) platform market with monopolistically competing fringe firms.
